Supplementary material for\\ A Benchmark of Named Entity Recognition Approaches in Historical Documents\\ Application to 19$^{th}$ Century French Directories

### 2022-01-20 src-latex/parts/10-introduction.tex
More typo fixes in intro

Being active research topics, OCR and named entity recognition (NER) are still difficult tasks when applied to historical text documents.
OCR approaches used for modern documents are likely to struggle even on printed historical documents due multiple causes related to text readability (low resolution scans, inconsistent printing rules, artifacts, show-through), document complexity (intricate and versatile page layout, use of ancient fonts \& special glyphs) and the variability inherent to the huge diversity of historical sources.
On the other hand, NER approaches developed for modern texts suffer from the time gap between the contemporary entities and the entities mentioned in older texts, and also from the errors introduced into the text by the OCR step.

@@

In a recent work to locate potentially polluted urban soils \cite{bell2020automated}, trade directories were leveraged to identify and locate all the gas stations in the city of Providence during the XX\textsuperscript{th} century.
The proposed information extraction pipeline extracts texts with OCR, identifies directories entries and recognizes business type and address within each entry.
In the same way, we aim at producing structured spatio-temporal data from Parisian trade directories.
These directories originate from several publishers, their content is organized following different indexing methods (by name, by activity or by address), printed in various layouts, use different fonts.
We therefore investigate several state-of-the-art OCR and NER approaches to assess their usability on the corpus.

>>>>

Being active research topics, OCR and named entity recognition (NER) are still difficult tasks when applied to historical text documents.
OCR approaches used for modern documents are likely to struggle even on printed historical documents due to multiple causes related to text readability (low resolution scans, inconsistent printing rules, artifacts, show-through), document complexity (intricate and versatile page layout, use of ancient fonts \& special glyphs) and the variability inherent to the huge diversity of historical sources.
On the other hand, NER approaches developed for modern texts suffer from the time gap between the contemporary entities and the entities mentioned in older texts, and also from the errors introduced into the text by the OCR step.

@@

In a recent work to locate potentially polluted urban soils \cite{bell2020automated}, trade directories were leveraged to identify and locate all the gas stations in the city of Providence during the XX\textsuperscript{th} century.
The proposed information extraction pipeline extracts texts with OCR, identifies directories entries and recognizes business type and address within each entry.
In the same way, we aim at producing structured spatio-temporal data from Parisian trade directories.
Because they originate from several publishers, their content is organized following different indexing methods (by name, by activity or by address), is printed in various layouts, and uses different fonts.
We therefore investigate several state-of-the-art OCR and NER approaches to assess their usability on the corpus.
